\documentclass{article}

%----------------------------------------------------------------------------------------
%	MARGINS
%----------------------------------------------------------------------------------------

\usepackage{geometry}
\geometry{
	paper=a4paper,
	top=2cm,
	bottom=2cm,
	left=2.5cm,
	right=2.5cm,
	headheight=14pt,
	footskip=1.5cm,
	headsep=1.2cm,
}

%----------------------------------------------------------------------------------------
%	FONT & GLOBALS
%----------------------------------------------------------------------------------------

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}

\usepackage{csquotes}

\usepackage{enumitem,amssymb}

\newlist{todolist}{itemize}{2}
\setlist[todolist]{label=$\square$}

\usepackage{pifont}

%----------------------------------------------------------------------------------------
%	COMMANDS
%----------------------------------------------------------------------------------------

\newcommand{\cmark}{\ding{51}}%
\newcommand{\xmark}{\ding{55}}%
\newcommand{\done}{\rlap{$\square$}{\raisebox{2pt}{\large\hspace{1pt}\cmark}}\hspace{-2.5pt}}
\newcommand{\wontfix}{\rlap{$\square$}{\large\hspace{1pt}\xmark}}

%----------------------------------------------------------------------------------------
%	DOCUMENT
%----------------------------------------------------------------------------------------

\title{
	\vspace{-1.5cm}
	{\centering\small{HS24 PREN1}\par}
	\textbf{Requirements - Simulator}
	\vspace{-1.3cm}
}

\begin{document}
\maketitle

\noindent
The main purpose of this document is to document the simulators requirements and track questions/details
that need to be addressed.

\begin{itemize}

  \item What exactly is the scope of the functionality that needs to be simulated?
  \begin{todolist}

  \item[\done] sensors? hardware emulation? \newline
        up to them team, defined in scope

  \item[\done] 3d or 2d graph model? what is expected? \newline
        again, up to the team, defined in scope

  \item[\done] does a physics engine need to be implemented/pulled in? \newline
        again, up to the team, defined in scope

  \end{todolist}

  \item Deployment \& ISA requirements/expectations
  \begin{todolist}

  \item[\done] on what hardware does the simulator need to run? \newline
        on the hardware of the team, is presented at the end

  \item[\done] is cross-compilation to other operating systems required? (linux, windows) \newline
        team has windows and linux, so needs to run on these 2 platforms

  \item[\wontfix] is cross-compilation to different architectures (isa) required? (x86, aarch64, risc-v) \newline
        not required, x86 is sufficient (however embedded hardware is probably not x86)

  \item[\done] how's the software distributed? (expectations of teachers) \newline
        teachers need to code in the repo, wont run it tho

  \item[\done] does the code need to be available to the teachers? \newline
        yes, in the repo

  \end{todolist}

  \item Necessary files (as defined by the document)
  \begin{todolist}

  \item[\done] what is needed in the first milestone? \newline
        nothing specifically

  \item[\done] seperate or incorparated \newline
        again, might be beneficial to incorparate it into the it-project

  \end{todolist}

\end{itemize}

\end{document}
